---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE, message = FALSE
)
```

# scatteR

<!-- badges: start -->
<!-- badges: end -->

scatteR generates scatterplots based on [scagnostic](https://cran.r-project.org/web/packages/scagnostics/index.html) measurements. The current implementation uses Simulated Annealing based on the GenSA package for optimization and rJava is required for the scagnostics measurement calculation.

## What are these scagnostics?

Simply put scagnostics are like diagnostics for scatterplots. Each scatterplot will have a certain set of characteristics that scagnostics will show to you. You can learn more about it through this [paper](https://www.semanticscholar.org/paper/Graph-theoretic-scagnostics-Wilkinson-Anand/8bc9868fe6c936614f7f94b01757723e9ffaaa43).

```{r}
library(palmerpenguins)
library(scagnostics)
plot(penguins$bill_length_mm,penguins$bill_depth_mm)
```
The above scatterplot has the following characteristics according to scagnostics.

```{r}
scagnostics(penguins$bill_length_mm,penguins$bill_depth_mm)
```

## Installation

You can install the released version of scatteR from [Github](https://github.com/janithwanni/scatteR) with:

``` r
install.packages("devtools")
devtools::install_github("janithwanni/scatteR")
```

## Example

### Simple usage

```{r example}
library(scatteR)
## basic example code
df <- scatteR(measurements = c("Monotonic" = 0.9),n_points = 100)
```

```{r}
scagnostics(df)
```

```{r}
plot(df$x,df$y)
```

### Integration into the tidy workflow

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
scatteR(c("Convex" = 0.9),n_points = 250,verbose=FALSE) %>% # data generation
  mutate(label = ifelse(y > x,"Upper","Lower")) %>% # data preprocessing
  ggplot(aes(x = x,y = y,color=label))+
  geom_point()+
  theme_minimal()+
  theme(legend.position = "bottom")
  
```

### Using scagnostics output to generate data

```{r}
generated <- scatteR(scagnostics(penguins$bill_length_mm,
                                 penguins$bill_depth_mm),
        n_points = length(penguins$bill_length_mm),verbose=FALSE)
penguins %>% 
  select(bill_length_mm,bill_depth_mm) %>% 
  drop_na() %>% 
  rename(x = bill_length_mm,y = bill_depth_mm) %>% 
  mutate(x = (x - min(x)) / (max(x) - min(x)),
         y = (y - min(y)) / (max(y) - min(y)),
         source = "penguins") %>% 
  bind_rows(generated %>% mutate(source = "generated")) %>% 
ggplot(aes(x = x,y = y,color=source))+
  geom_point()+
  theme_minimal()+
  theme(legend.position = "bottom")
```

