---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE, message = FALSE
)
```

# scatteR

<!-- badges: start -->
<!-- badges: end -->

scatteR generates scatterplots based on [scagnostic](https://cran.r-project.org/web/packages/scagnostics/index.html) measurements. The current implementation uses Simulated Annealing based on the GenSA package for optimization and rJava is required for the scagnostics measurement calculation.

## What are these scagnostics?

Simply put scagnostics are like diagnostics for scatterplots

## Installation

You can install the released version of scatteR from [Github](https://github.com/janithwanni/scatteR) with:

``` r
install.packages("devtools")
devtools::install_github("janithwanni/scatteR")
```

## Example

### Simple usage

```{r example}
library(scatteR)
## basic example code
df <- scatteR(measurements = c("Monotonic" = 0.9),n_points = 100)
```

```{r}
library(scagnostics)
scagnostics(df)
```

```{r}
plot(df$x,df$y)
```

### Integration into the tidy workflow

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
scatteR(c("Convex" = 0.9),n_points = 250) %>% # data generation
  mutate(label = ifelse(y > x,"Upper","Lower")) %>% # data preprocessing
  ggplot(aes(x = x,y = y,color=label))+
  geom_point()+
  theme_minimal()+
  theme(legend.position = "bottom")
  
```

